Figures

### 2019-07-12 code/figures.rmd
Changed Figure 3 into correlations per effect-type

```{r transform_effect_and_compute_rma}
#Transform effect sizes to biserial correlations (pearson's correlations as is)
#then compute random effects meta-analyses per effect
#'transform_MA' and 'summarizer' are sourced functions
res <- dat %>% 
  split(.$effect) %>%  #necessary step otherwise the function is applied overall
  map(transform_MA) %>% #apply function each effect in the list
  map_dfr(summarizer, .id = "effect") %>%  #apply function and transform to dataframe
  mutate(r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

```{r cor_het_effect_size, results = "hide", cache=TRUE}
#Basic correlations
cor.test(res$I2, res$r) #pearson I2

I2_fit <- summary(lm(I2 ~ r, data = res)) #for annotating figures

cor.test(res$tau2, res$r) #pearson tau2

tau2_fit <- summary(lm(tau2 ~ r, data = res))

cor.test(res$H2, res$r) #pearson H2

H2_fit <- summary(lm(H2 ~ r, data = res))

cor.test(res$I2, res$r, method = "spearman") #spearman

##Excluding anchoring effects
dropped_anchoring <- res %>%
  filter(!grepl("Anchoring", effect))

cor.test(dropped_anchoring$I2, dropped_anchoring$r) #pearson

@@

#I2
pear <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + r, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + I2)

I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ I2 + r, data=d, method = "spearman")
     return(fit$estimate)
}

options(warn=-1)
bootfit <- boot(data=res, statistic=spear, R=1000, formula= ~ r + I2)
options(warn=0)

@@

#Excluding anchoring effects
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ r + I2)

#H2
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ H2 + r, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=res, statistic=pear, R=1000, formula= ~ r + H2)

@@

##Figure 3
```{r plot_res, cache = TRUE}

#Plots of H2 and I2 vs. biserial correlation r for all effects together, two above chunks need to be run first

I2 <- ggplot(res, aes(x = r, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  annotate("text", x = 0.14, y = Inf, vjust = 5, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = NULL)

H2 <- ggplot(res, aes(x = r, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(axis.text.x = element_blank(), #drop x-axis labels in preparation for combining plots
        axis.ticks.x = element_blank(),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = NULL)

tau2 <- ggplot(res, aes(x = r, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  annotate("text", x = 0.14, y = Inf, vjust = 5, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  theme(panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) +
  scale_y_continuous(name = expression(paste(italic(tau)^2, " estimate"))) +
  scale_x_continuous(name = expression(paste("Biserial and Pearson's correlations ")))

effect_het <- plot_grid(I2, H2, tau2, ncol = 1, align = "v", rel_heights = c(0.86, 0.86, 1), labels = c("a", "b", "c")) #combine plots
effect_het
# save_plot("../figures/effect-het.png", effect_het,
         # ncol = 1, base_height = 7, base_width = 5, dpi = 600)

Figure 3. The correlation between a) I2 ,and effect size and b) H2 and c)  τ ̂^2and effect size for 37 effects from ten pre-registered multi-lab replication projects. Shaded bands represent 95% confidence intervals

##Correlations per effect type (alternative figure 3, probably drop)
```{r corr_per_effect_type, cache = TRUE}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

#effects that were transformed from OR to SMD
OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR

OR_fit <- function(x){ #fit rma to odds raios
  fit <- rma(measure = "OR", ai = outcome_t1, bi = outcome_t2, ci = outcome_c1, di = outcome_c2, n1i = ntreatment, n2i = ncontrol,  data = x)
  hetero <- confint(fit)$random[c(1, 3), ] 
  data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3])}

fit_OR <- dat %>% 
  filter(effect %in% OR2d) %>% 
  split(.$effect) %>% 
  map_dfr(OR_fit, .id = "effect")

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% 
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference",
                              'Raw mean difference' = "Mean Difference",
                              'Risk difference' = "Risk Difference",
                              'r' = "Correlation")) %>% 
  left_join(tau2_per_type) %>% 
  filter(!effect %in% OR2d) %>% #drop old SMD converted OR
  bind_rows(fit_OR) %>% #and instead add OR meta-analyzed as OR
  mutate(effect_type = ifelse(is.na(effect_type), "Odds Ratio", effect_type),
         eff_size = abs(eff_size)) #need the absolute values for plotting

fitter <- function(df){ #function to fit correlations for annotating facet plots
 fit <- summary(lm(tau2 ~ eff_size, data = df))
 data.frame(b = format(round(fit$coefficients[2, 1], digits = 2), nsmall = 2), #because map_dfr requires dataframe
            r = format(round(sqrt(fit$r.squared), digits = 2), nsmall = 2)) #output, the output is kept as two vars
}

labels <- tau2_per_type %>% 
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>% 
  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting

tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_line(stat = "smooth", method = "lm", se = FALSE, color = "black", alpha = .5, linetype = "dashed") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels, aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 6, size = 3.5, fontface = "italic") + #hjust and vjust can be used to annotate the same position in all facets
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, scales = "free") #use free scales since scales are different

tau2_facet
# ggsave("../figures/tau2_facet.png", dpi = 600, height =  7, width = 7)

>>>>

##Figure 3, correlations per effect type
```{r corr_per_effect_type, cache = FALSE}
#Each set of input datapoints is meta-analyzed as per the original replication project
#Then correlated with tau2 per effect type
#Function 'est_heterogen_smd_raw' is sourced, see also tables.rmd
tau2_per_type <- dat %>% 
  split(.$effect) %>%  
  map_dfr(est_heterogen_smd_raw, .id = "effect")

MD_fit <- function(x){
    fit <- rma(measure = "SMD", m1i = outcome_t1, m2i = outcome_c1, sd1i = outcome_t2, sd2i = outcome_c2, n1i = ntreatment, n2i = ncontrol, data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
}

fisher_fit <- function(x){
    fit <- rma(measure = "ZCOR", ri = effect_size, ni = Ntotal, data = x)
    hetero <- confint(fit)$random[c(1, 3), ] 
    data.frame(eff_size = fit$b[[1]], #effect size (point estimate) 
             s_I2 = hetero[2, 1], s_ci.lb = hetero[2, 2], s_ci.ub = hetero[2, 3],
             tau2 = hetero[1, 1], tau2_ci.lb = hetero[1, 2], tau2_ci.ub = hetero[1, 3],
             H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1))
    }

#Raw mean differences to SMD
MD_standardized <- dat %>% 
  filter(effect_type == "Raw mean difference" & !outcomes1_2 == "mean _ SE") %>% #No method in metafor to compute SMD when standard deviations not given, so skip this study 
  split(.$effect) %>% 
  map_dfr(MD_fit, .id = "effect")

fisher <- dat %>% 
  filter(effect_type == "r") %>% 
  split(.$effect) %>% 
  map_dfr(fisher_fit, .id = "effect")

#effects that were transformed from OR to SMD by ML1 which we will drop
OR2d <- c('Allowed vs. forbidden', 'Gain vs. loss framing', #originally transformed to SMD
           'Norm of reciprocity', 'Low vs. high category scales') #refit as OR

tau2_per_type <- dat %>% #This is to add the effect_type names
  select(effect, effect_type) %>% 
  distinct() %>% #get unique rows
  mutate(effect_type = recode(effect_type, 
                              d = "Standardized Mean Difference")) %>% 
  left_join(tau2_per_type) %>% #Add the meta-analytic results
  filter(!effect %in% c(OR2d, MD_standardized$effect, fisher$effect)) %>% #drop old SMD converted OR, unstandardized MD and raw correlations
  bind_rows(MD_standardized) %>% #add MD after standardization
  bind_rows(fisher) %>% #add correlations as fisher's z
  mutate(effect_type = ifelse(effect %in% MD_standardized$effect, "Standardized Mean Difference", effect_type),
         effect_type = ifelse(effect %in% fisher$effect, "Fisher's z", effect_type),
         eff_size = abs(eff_size)) %>% #need the absolute values for plotting
  filter(effect_type %in% c("Standardized Mean Difference", "Fisher's z"))

fitter <- function(df){  #function to fit correlations for annotating facet plots
 fit_tau2 <- summary(lm(tau2 ~ eff_size, data = df))
 fit_I2 <- summary(lm(s_I2 ~ eff_size, data = df))
 fit_H2 <- summary(lm(H2 ~ eff_size, data = df))
 b <- c(fit_tau2$coefficients[2, 1], fit_I2$coefficients[2, 1], fit_H2$coefficients[2, 1])
 r <- c(sqrt(fit_tau2$r.squared), sqrt(fit_I2$r.squared), sqrt(fit_H2$r.squared))
 data.frame(b = format(round(b, digits = 2), nsmall = 2), #because map_dfr requires dataframe
            r = format(round(r, digits = 2), nsmall = 2),
            index = c("tau2", "I2", "H2")) #output, the output is kept as two vars
}

labels <- tau2_per_type %>% #row 1:2 = tau2, row 3:4 = I2, row 5:6 = H2
  split(.$effect_type) %>% 
  map_dfr(fitter, .id = "effect_type") %>%
  mutate(lab = paste0("b = ", b, ", r = ", r)) #put output into one variable for improved plotting

#tau2plot----
tau2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = tau2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "tau2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#I2plot----
I2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = s_I2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "I2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(I)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  coord_cartesian(ylim = c(0, 100)) +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#H2plot----
H2_facet <- ggplot(tau2_per_type, aes(x = eff_size, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") + #to set alpha for the line geom_line must be used rather than geom_smooth
  geom_text(data = labels[labels$index == "H2",], aes(label = lab), x = -Inf, y = Inf, hjust = -0.1, vjust = 2, size = 3.5, fontface = "italic", alpha = .6) + #hjust and vjust can be used to annotate the same position in all facets even though the scale are different
  scale_y_continuous(name = expression(paste(italic(H)^2, " Index"))) +
  scale_x_continuous(name = "Effect size") +
  theme_classic() +
  theme(strip.background = element_blank(), #remove box around titles
        strip.text = element_text(size = 12),
        panel.border = element_rect(fill = NA, colour = "black", #add box around plots
                                    size = 0.5, linetype = "solid")) + 
  facet_wrap(~effect_type, nrow = 2, scales = "free") #use free scales since scales are different

#combined----
combo <- cowplot::plot_grid(tau2_facet, I2_facet, H2_facet, labels = "AUTO")
#ggsave("../figures/effect-het.png", dpi = 600, height =  7, width = 7)
combo
```

Figure 3. The correlation between effect size and A) tau2, b) I2 and c) H2 respectively  22 effects that were measured as mean or standardized mean differences and 6 effects measured as correlations from ten pre-registered multi-lab replication projects. Effects reported as mean differences were standardized and correlations were transformed into Fisher’s z. Shaded bands represent 95% confidence intervals

```{r cor_het_effect_size, results = "hide", cache=TRUE}

#1. Standardized mean differences----
SMDs <- tau2_per_type %>% filter(effect_type == "Standardized Mean Difference")

cor.test(SMDs$tau2, SMDs$eff_size) #pearson tau2
cor.test(SMDs$s_I2, SMDs$eff_size) #pearson I2
cor.test(SMDs$H2, SMDs$eff_size) #pearson H2

cor.test(SMDs$tau2, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$s_I2, SMDs$eff_size, method = "spearman") #spearman
cor.test(SMDs$H2, SMDs$eff_size, method = "spearman") #spearman

##Excluding anchoring effects
dropped_anchoring <- SMDs %>%
  filter(!grepl("Anchoring", effect))

cor.test(dropped_anchoring$s_I2, dropped_anchoring$eff_size) #pearson

@@

#1.1 I2 confidence intervals----
pear <- function(formula, data, indices){ #pearson
     d <- data[indices,]
     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=SMDs, statistic=pear, R=1000, formula= ~ eff_size + s_I2)
I2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#Excluding anchoring effects
bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + s_I2)

#1.2 Tau2 confidence intervals----
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau2 + eff_size, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + tau2)

tau2_ci_pears <- boot.ci(bootfit, type=c("perc", "bca"))

#Excluding anchoring effects
cor.test(dropped_anchoring$tau2, dropped_anchoring$eff_size)

bootfit <- boot(data=dropped_anchoring, statistic=pear, R=1000, formula= ~ eff_size + tau2)

tau2_dropped_ci_pears <- boot.ci(bootfit, type=c("perc", "bca")) #percentile and adjusted percental method (BCa)

#1.3 H2 confidence intervals----
pear <- function(formula, data, indices){
     d <- data[indices,]
     fit <- cor.test(formula = ~ H2 + eff_size, data=d)
     return(fit$estimate)
}

bootfit <- boot(data=tau2_per_type, statistic=pear, R=1000, formula= ~ eff_size + H2)

#1.4 spearman bootstrap CIs----
#First for I2
spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ s_I2 + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + s_I2)
options(warn=0)

@@

#Second for tau2
spear <- function(formula, data, indices){ #spearman
     d <- data[indices,]
     fit <- cor.test(formula = ~ tau2 + eff_size, data=d, method = "spearman")
     return(fit$estimate)
}

options(warn=-1)
bootfit <- boot(data=tau2_per_type, statistic=spear, R=1000, formula= ~ eff_size + tau2)
options(warn=0)

tau2_ci_spear <- boot.ci(bootfit, type=c("perc", "bca"))

#2. Fisher's z----
fish <- tau2_per_type %>% filter(effect_type == "Fisher's z" )
cor.test(fish$tau2, fish$eff_size) #pearson tau2
cor.test(fish$s_I2, fish$eff_size) #pearson I2
cor.test(fish$H2, fish$eff_size)

@@
